### 2021-11-14 paper/manuscript.Rmd
Update results, add images

# Results
There were 3888 condition combinations and for each of those the algorithms ran 100 times, leaving 388800 cases to analyze. Out of those, 20 cases had missing values on all metrics for the RMA algorithm. Closer inspection showed that both the cubic and exponential model each contributed ten times to the missing values and only when 2, 3 or 6 moderators were taken up in the model. However, since these 20 cases make up only 0.005% of the data, the missing values were chosen to be omitted from further analysis. Another observation is that the two-way interaction model only had results when there were either 3,4 or 7 moderators taken up, while the other models only had results when there were 2,3 or 6 moderators. It is therefor more challenging to compare and interpret the effect the moderators had on the performance criteria between the two-way interaction and the other models.

@@

To determine the effect of the design factors on $R^2$ for all algorithms, four separate ANOVA’s were performed, one per algorithm. The effect size $\eta^{2}$ per condition per algorithm, including for all two-way interactions can be found in table 1. Do note that the ANOVA's were performed with the normality assumption violated. The estimates serve mostly as a guidance, rather than an absolute result.

Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on $R^{2}$ for all algorithms. As $\beta$ increased, the performance of all algorithms increased as well. However, $\beta$ did interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model. The image of the interaction is shown in image 1. When the exponential and cubic model were estimated, the increase of $R^{2}$ slows for every higher value of $\beta$. For the estimation of the two-way interaction model the increase only slowed when $\beta$ goes from 0.5 to 0.8, while the steepest increase for the linear model estimation is when $\beta$ increases from 0.2 to 0.5. Also noteworthy is that $R^2$ stagnates during estimation of the cubic model as $\beta$ goes up to 0.5 and onwards, while the other models do keep increasing. There was little difference in median $R^2$ between Horsehoe, Lasso and RMA, while MetaForest performed worst.

The second largest marginal effect was that of the estimated model. All algorithms had the highest $R^2$ under the cubic model, followed by a similar performance on the two-way interaction and exponential models. All algorithms performed worst for the linear model. There again was little difference in performance between the Pema algorithms and RMA, although MetaForest performed worst. Image 2 shows the relationship.

There also was a moderate interaction effect between the estimated model and the amount of skewness of the input data $\alpha$, especially for the Pema algorithms. Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions. Most obvious to note is that all algorithms, except for when the linear model was estimated, generally performed better on more skewed data, although the algorithms did perform worse during estimation of the two-way interaction model and as $\alpha$ goes from 5 to 10. Overall performance was best during estimation of the cubic model, but the performance difference between estimated models decreased as $\alpha$ increased. Image 3 shows the relationship.

The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. That is, as $\tau^{2}$ increased, $R^{2}$ decreased. Image 4 shows the relationship.

The mean sample size per study $\bar{n}$ also had a moderate effect. For all algorithms the effect of $\bar{n}$ was positively linearly related with $R^{2}$. Again, the Pema and RMA algorithms performed better than MetaForest. Image 5 shows the relationship.

An especially large effect was found for the number of studies used in the training data $\kappa$ for MetaForest, $\eta^{2} = 0.27$, while this effect was substantially smaller for RMA, $\eta^{2} = 0.11$; Lasso, $\eta^{2} = 0.06$ and; Horseshoe, $\eta^{2} = 0.05$. The relationship is positively linear for all algorithms, but the slope is especially steep for MetaForest. Image 6 shows the relationship.

Finally, the number of moderators did not have a big effect for the Pema algorithms: $\eta^{2} = 0.01$ while for RMA and MetaForest $\eta^{2} = 0.05$. The relationship is shown in image 7. The relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except MetaForest. This increase in performance for MetaForest appears when the number of moderators go from 3 to 4.

@@

The biggest predictor on the correct estimation of $\tau^{2}$ was the estimated model. This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms. Image 8 shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ . It becomes more clear why this overestimation occurred when showing the interaction between $\beta$ and the model estimated on $\Delta\tau^{2}$, shown in image 9. First note the general trend that during estimation of all models $\tau^{2}$ got more overestimated as $\beta$ increased, except during estimation of the linear model, where the effect of $\beta$ on $\Delta\tau^{2}$ was close to zero, except for MetaForest. However, note the scales for the y-axes. While estimating the two-way interaction, linear and exponential model, $\Delta\tau^2$ stayed well within a confined interval. However, the algorithms severely overestimated $\tau^{2}$ when the model contained cubic terms. Especially MetaForest overestimated $\tau^{2}$ substantially when $\beta = 0.8$ and the estimated model is cubic: $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$. The other algorithms also had a $\Delta\tau^{2} > 1$ in these conditions, but the results were not as severe. Interestingly, the Pema algorithms even outperformed the RMA algorithm in these conditions.

The marginal effects of $\beta$ on $\Delta\tau^{2}$  are shown in image 10. MetaForest was most affected by the increase in $\beta$, but in general performed better than the Pema algorithms when $\beta < 0.8$. The RMA algorithm performed best overall.

The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, although there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased. However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added. Image 11 shows this interaction. The algorithms were rather unaffected by $\alpha$ for the linear model, and a small decrease in $\Delta\tau^{2}$ as $\alpha$ increased can be seen in the exponential model. When the two-way interaction model is estimated however, the algorithms benefitted as $\alpha$ increased, while for the cubic model, $\Delta\tau^{2}$ first increased as $\alpha$ increased from 0 to 2, but decreased as $\alpha$ increased from 2 to 10. RMA performed best, followed by MetaForest. The Pema algorithms performed similarly, but worst.

The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$ was rather unnoticeable for the RMA and MetaForest algorithms. The tendency for the Pema algorithms on the other hand, was to overestimate $\tau^{2}$ more as the true $\tau^{2}$ increased. Image 12 shows the marginal relationship.

The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either. A small increase in $\Delta\tau^{2}$ can be seen in the RMA and MetaForest algorithm as the number of moderators increased, which was not found for the Pema algorithms. However, A small note is that MetaForest did substantially increase in $\Delta\tau^{2}$ as more moderators were added and the estimated model is cubic. Image 13 shows the interaction between the number of moderators and the estimated model.

$\kappa$ only had a substantial effect for MetaForest; the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated. For the other algorithms, decreasing $\kappa$ had little to no effect on correctly estimating the residual heterogeneity. Image 14 shows the relationship.

Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$. Image 15 shows the marginal relationship.

@@

There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithms it did not matter which interval type was analyzed. It was found that MetaForest had the highest proportion true positives: $TP_{Mf} = 0.98$, closely followed by RMA: $TP_{RMA} = 0.96$. Horshoe performed slightly better than Lasso;  $TP_{Hs} = 0.91$; $TP_{Lasso} = 0.89$. As for $TN$, it was found that the pema algorithms performed best: $TN_{Hs} \ \text{and} \ TN_{Lasso} = 0.93$, followed by RMA: $TN_{RMA} = 0.89 \pm 0.20$. MetaForest performed worst by a large margin: $TN_{Mf} = 0.50$. The Mean Absolute Deviation for all algorithms on both $TP$ and $TN$ was 0, except for MetaForests performance on $TN$, where the Mean Absolute Deviation was 0.44.

@@

Firstly, $\kappa$ only had a marginal positive effect on $TP$. As $\kappa$ increased, $TP$ also increased. MetaForest had the highest $TP$, followed by RMA and, lastly, Horsehoe and Lasso. The increase in $TP$ for higher values of $\kappa$ was steeper for the Pema algorithms, however. There was also an interaction of $\kappa$ with the estimated model shown in image 16. During estimation of the linear and two-way interaction model, the relationship of $\kappa$ looked relatively linear. At $\kappa = 20$ the $TP$ was relatively low for the algorithms, compared to the cubic model where $TP$ starts at .98 and converges to 1 as $\kappa$ increased. This latter relationship was also found for the exponential model, although the $TP$ at $\kappa = 20$ was lower.

$\bar{n}$ had a positive and roughly linear relationship with $TP$ for all algorithms. MetaForest performed best, followed by RMA, while Horseshoe and Lasso performed worst. Image 17 shows the relationship.

$\beta$ had an interaction effect with the model estimated on $TN$. Only during estimation of the two-way interaction model, $TN$ decreased as $\beta$ increased, For the other models, $TN$ remained stable. This could be because the interaction model was only fitted when there were 3,4 or 7 moderators, while for the other models, only 2,3 or 6 moderators were used. Image 18 shows the relationship. The effect of $\beta$ on $TP$ was positive; as $\beta$ increased, $TP$ increased too.

The true $\tau^2$ had a negative effect on $TP$, while $\alpha$ seemed to have little effect on both $TP$ and $TN$. Image 19 shows the marginal relationship of $\tau^2$ on $TP$.

Finally, there was an effect of number of moderators on $TN$, but only for the two-way interaction model. The $TN$ increased as the number of moderators did. Image 20 shows the interaction. This relationship was reversed for $TP$ and was found for all algorithms, i.e. $TP$ decreased as the number of moderators increased.

>>>>

# Results
There were 3888 condition combinations in total. The algorithms ran on 100 different datasets on each of those, leaving 388800 cases to analyze. There were 20 of those cases for which the RMA algorithm had missing values on all metrics. Closer inspection showed that both the cubic and exponential model each contributed ten times to the missing values and only when 2, 3 or 6 moderators were taken up in the model. However, since the missing cases make up only 0.005% of the data, the cases were chosen to be omitted from further analysis entirely. Another observation is that the two-way interaction model only had results when the number of moderators in the model was either 3, 4 or 7, while the other models only had results when there were 2, 3 or 6 moderators. It is therefor more challenging to compare and interpret the effect the moderators had on the performance criteria between the two-way interaction and the other models.

@@

To determine the effect of the design factors on $R^2$ for all algorithms, four separate ANOVA’s were performed; one per algorithm. The effect size $\eta^{2}$ per condition per algorithm, including for all two-way interactions can be found in table 1. Do note that the ANOVA's were performed with the normality assumption violated. The estimates serve mostly as a guidance, rather than an absolute result.

Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on $R^{2}$ for all algorithms. As $\beta$ increased, the performance of all algorithms increased as well. However, $\beta$ did interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model. A graphical representation of the interaction is shown in image 1. When the exponential and cubic model were estimated, the increase of $R^{2}$ slowed for every higher value of $\beta$. For the estimation of the two-way interaction model the increase only slowed when $\beta$ went from 0.5 to 0.8, while the steepest increase for the linear model estimation was when $\beta$ increased from 0.2 to 0.5. Also noteworthy is that $R^2$ stagnated during estimation of the cubic model as $\beta$ went up to 0.5, while for the other models $R^2$ did keep increasing. There was little difference in median $R^2$ between Horsehoe, Lasso and RMA, while MetaForest performed worst.

The second largest marginal effect was that of the estimated model. All algorithms had the highest $R^2$ under the cubic model, followed by a similar performance on the two-way interaction and exponential models. All algorithms performed worst for the linear model. There again was little difference in performance between the Pema algorithms and RMA, although MetaForest performed worst. Image 2A shows the relationship.

There also was a moderate interaction effect between the estimated model and the amount of skewness of the input data $\alpha$, especially for the Pema algorithms. Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions. Most obvious to note is that all algorithms, except for when the linear model was estimated, generally performed better on more skewed data, although the algorithms did perform worse during estimation of the two-way interaction model when $\alpha$ went from 5 to 10. Overall performance was best during estimation of the cubic model, but the performance difference between estimated models decreased as $\alpha$ increased. Image 3 shows the relationship.

The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. That is, as $\tau^{2}$ increased, $R^{2}$ decreased. Image 2B shows the relationship.

The mean sample size per study $\bar{n}$ also had a moderate effect. For all algorithms the effect of $\bar{n}$ was positively linearly related with $R^{2}$. Again, the Pema and RMA algorithms performed better than MetaForest. Image 2C shows the relationship.

An especially large effect was found for the number of studies used in the training data $\kappa$ for MetaForest, while this effect was substantially smaller for RMA, Lasso and Horseshoe. The relationship is positively linear for all algorithms, but the slope is especially steep for MetaForest. Image 2D shows the relationship.

Finally, the number of moderators did not have a big effect for the Pema algorithms, while for RMA and MetaForest the effect was more noticeable. The relationship is shown in image 7. The relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except MetaForest. This increase in performance for MetaForest appears when the number of moderators go from 3 to 4.

@@

The biggest predictor on the correct estimation of $\tau^{2}$ was the estimated model. This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms. Image 5A shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ . It becomes more clear why this overestimation occurred when showing the interaction between $\beta$ and the model estimated on $\Delta\tau^{2}$, shown in image 6. First note the general trend that during estimation of all models $\tau^{2}$ got more overestimated as $\beta$ increased, except during estimation of the linear model, where the effect of $\beta$ on $\Delta\tau^{2}$ was close to zero, except for MetaForest. However, note the scales for the y-axes. While estimating the two-way interaction, linear and exponential model, $\Delta\tau^2$ stayed well within a confined interval. However, the algorithms severely overestimated $\tau^{2}$ when the model contained cubic terms. Especially MetaForest overestimated $\tau^{2}$ substantially when $\beta = 0.8$ and the estimated model is cubic: $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$. The other algorithms also had a $\Delta\tau^{2} > 1$ in these conditions, but the results were not as severe. Interestingly, the Pema algorithms even outperformed the RMA algorithm in these conditions.

The marginal effects of $\beta$ on $\Delta\tau^{2}$ are shown in image 5B. MetaForest was affected most by the increase in $\beta$, but in general performed better than the Pema algorithms when $\beta < 0.8$. The RMA algorithm performed best overall.

The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, although there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased. However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added. Image 7 shows this interaction. The algorithms were rather unaffected by $\alpha$ for the linear model, and a small decrease in $\Delta\tau^{2}$ as $\alpha$ increased can be seen in the exponential model. When the two-way interaction model was estimated however, the algorithms benefitted as $\alpha$ increased, while for the cubic model, $\Delta\tau^{2}$ first increased as $\alpha$ increased from 0 to 2, but decreased as $\alpha$ increased from 2 to 10. RMA performed best, followed by MetaForest. The Pema algorithms performed similarly, but worst.

The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$ was rather unnoticeable for the RMA and MetaForest algorithms. The tendency for the Pema algorithms on the other hand, was to overestimate $\tau^{2}$ more as the true $\tau^{2}$ increased. Image 5C shows the marginal relationship.

The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either. A small increase in $\Delta\tau^{2}$ can be seen in the RMA and MetaForest algorithm as the number of moderators increased which was not found for the Pema algorithms. However, A small note is that MetaForest did substantially increase in $\Delta\tau^{2}$ as more moderators were added and the estimated model is cubic. Image 8 shows the interaction between the number of moderators and the estimated model.

$\kappa$ only had a substantial effect for MetaForest; the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated. For the other algorithms, decreasing $\kappa$ had little to no effect on correctly estimating the residual heterogeneity. Image 9 shows the interaction of $\kappa$ with the estimated model.

Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$. Image 5D shows the marginal relationship.

@@

There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithms it did not matter which interval type was analyzed. It was found that MetaForest had the highest proportion true positives: $TP_{Mf} = 0.98$, closely followed by RMA: $TP_{RMA} = 0.96$. Horshoe performed slightly better than Lasso;  $TP_{Hs} = 0.91$; $TP_{Lasso} = 0.89$. As for $TN$, it was found that the pema algorithms performed best: $TN_{Hs} \ \text{and} \ TN_{Lasso} = 0.93$, followed by RMA: $TN_{RMA} = 0.89$. MetaForest performed worst by a large margin: $TN_{Mf} = 0.50$. The Mean Absolute Deviation for all algorithms on both $TP$ and $TN$ was 0, except for MetaForests performance on $TN$, where the Mean Absolute Deviation was 0.44.

@@

Firstly, $\kappa$ only had a positive effect on $TP$. As $\kappa$ increased, $TP$ also increased. MetaForest had the highest $TP$, followed by RMA and, lastly, Horsehoe and Lasso. The increase in $TP$ for higher values of $\kappa$ was steeper for the Pema algorithms, however. There was also an interaction of $\kappa$ with the estimated model shown in image 10. During estimation of the linear and two-way interaction model, the relationship of $\kappa$ looked relatively linear. At $\kappa = 20$ the $TP$ was relatively low for the algorithms, compared to the cubic model where $TP$ starts at .98 and converges to 1 as $\kappa$ increased. This latter relationship was also found for the exponential model, although the $TP$ at $\kappa = 20$ was lower.

$\bar{n}$ had a positive and roughly linear relationship with $TP$ for all algorithms. MetaForest performed best, followed by RMA, while Horseshoe and Lasso performed worst. Image 11A shows the relationship.

$\beta$ had an interaction effect with the model estimated on $TN$. Only during estimation of the two-way interaction model, $TN$ decreased as $\beta$ increased, For the other models, $TN$ remained stable. This could be because the interaction model was only fitted when there were 3,4 or 7 moderators, while for the other models, only 2,3 or 6 moderators were used. Image 12 shows the relationship. The effect of $\beta$ on $TP$ was positive; as $\beta$ increased, $TP$ increased too.

The true $\tau^2$ had a negative effect on $TP$, while $\alpha$ seemed to have little effect on both $TP$ and $TN$. Image 11B shows the marginal relationship of $\tau^2$ on $TP$.

Finally, there was an effect of number of moderators on $TN$, but only for the two-way interaction model. The $TN$ increased as the number of moderators did. Image 13 shows the interaction. This relationship was reversed for $TP$ and was found during estimation of all models, i.e. $TP$ decreased as the number of moderators increased. Image 14 shows the relationship.
